\chapter*{Executive Summary}
\addcontentsline{toc}{chapter}{Executive Summary}
The nuclear fuel performance code, FAST, has been co-developed by the U.S.  Nuclear Regulatory
Commission and Pacific Northwest National Laboratory as a confirmatory tool designed to calculate
the steady-state and transient fuel behavior at high burnup (up to rod-average burnup of
\SInum{62}{GWD/MTU}, depending on application). The code is an evolution of the former PNNL
developed codes FRAPCON and FRAPTRAN, which were used to calculate the steady-state and transient
response of LWR fuel rods, respectively. This document is Volume 1 of a three-volume series that
describes the current version of FAST. Volume 1 contains: 
\begin{enumerate}
    \item Code limitations and structure 
    \item Fuel performance model summaries; and 
    \item Code input instructions and features to aid the user. 
\end{enumerate}

Volume 2 (\colorbox{yellow}{Geelhood et al, 2018}) provides a code assessment based on comparisons
of code predictions to integral performance data up to high burnup. Volume 3
(\colorbox{yellow}{Gellhood et al, 2018}) provides a description and assessment of the material
models used by FAST's material library, MatLib.
\\
\\
The FAST code is designed to perform steady-state and transient fuel rod calculations. The code uses
a single-channel coolant enthalpy rise model.  The code uses a finite difference heat conduction
model, which uses a variable mesh spacing in the fuel material to accommodate for the power peaking
at the pellet edge that occurs in high-burnup fuel.
\\
\\
FAST has been validated for boiling-water reactors, pressurized reactors, and heavy-water reactors.
The fuels that have been validated are uranium dioxide (\element{U}{}\element{O}{2}), mixed oxide
fuel ((\element{U}{},\element{Pu}{})\element{O}{2}), urania-gadolinia
(\UO-\element{Gd}{2}\element{O}{3}), and \UO with zirconium diboride (\element{ZrB}{2}) coatings.
The cladding types that have been validated are Zircaloy-2, Zircaloy-4, M5, ZIRLO, and Optimized
ZIRLO.  FAST-1.0 can predict fuel and cladding temperature, rod internal pressure, fission gas
release, cladding axial and hoop strain, and cladding corrosion and hydriding. The code uses an
updated version of the MATPRO material properties package (\cite{ref:Hagrman1981a})
as described in a separate material properties handbook (\cite{ref:Luscher2014b}),
that has been updated for high-burnup conditions and advanced cladding alloys.
\newpage\null
{}
